Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
CModel colors

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This Figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of the \cmodel{} color}

    Consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial  for photometric redshift and spectral energy distribution (SED) estimates. They are also key, for example, to the selection of high-$z$ Lyman-break galaxies (LBG) .

    Fig \ref{fig:cmodel_color} evaluates the  accuracy of \forced{} $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as Figure Fig \ref{fig:psf_color}. We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    The $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for the entire range of magnitudes and colors that we have tested.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower $y$ band imaging depth. Highly blended galaxies have larger uncertainties in their colors compared to isolated galaxies.  Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors compared to their input colors.

Figure  \ref{fig:cmodel_cdist} compare the input color--color distributions with the recovered color distributions. The general 2--D distributions are well recovered but the accuracy is not as good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors in the redder filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

We note that  our synthetic galaxies do not have color gradients.  In reality, color gradients will complicate the situation and hence the uncertainties shown here should be considered as lower limits.

>>>>

    The \s2n{} for PSF photometry is defined as
    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
    in the $g$- and $i$-bands. 
    This Figure shows the expected \s2n{} of stars as a function of magnitude in the 
    Wide layer.
    The slopes and scatters of these relations are very similar to the ones using 
    real stars on these two \tracts{}.

@@

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Precision and Accuracy of the \cmodel{} color}

    Precise and unbiased five-band \cmodel{} colors from \hscpipe{} are crucial for
    photometric redshift estimates and spectral energy distribution (SED) fitting 
    results. 
    They are also key, for example, to the selection of high-$z$ Lyman-break 
    galaxies (LBG).

    Fig \ref{fig:cmodel_color} evaluates the precision and accuracy of \forced{} 
    $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as 
    Fig \ref{fig:psf_color}. 
    We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ 
    mag is ${\sim}0.04$ mag.
    The statistical uncertainty increases to ${\sim}0.11$ mag at 
    $i_{\mathrm{Input}}{\sim}25.0$ mag.
    The $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for the entire range of magnitudes and colors that we have tested.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower $y$ band 
    imaging depth. 
    Highly blended galaxies are less precise in their \forced{} \cmodel{} colors 
    compared to isolated galaxies.  
    Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors compared to their input colors.

    Fig \ref{fig:cmodel_cdist} compare the input color--color distributions with the
    recovered ones. 
    The general 2--D distributions are well recovered but the precision is not as 
    good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors in the redder 
    filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

    We note that our synthetic galaxies do not have color gradients.  
    In reality, color gradients will complicate the situation and hence the statistical 
    uncertainties shown here should be considered as lower limits.
